---
title: "R Notebook"
output:
  html_document:
    df_print: paged
---

```{r}
cbPalette <- c("#999999", "#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7")
library(readr)
library(tidyverse)
library(scales)
library(ggrepel)

export <- read_csv("export.csv")


ds <- export %>% 
  mutate(date = as.Date(.$`Recorded Date`, format = "%d/%m/%y"),
         social_from = Social,
         social_follow = .$`Where do you follow the FT on social media?`,
         follow_reason = .$`What is your main reason for following the FT on social media? - Selected Choice`,
         follow_reason_alt = .$`What is your main reason for following the FT on social media? - Other (please specify) - Text`,
         content_associate = .$`Which of the following content do you associate with the FT? (Select any that apply) - Selected Choice`,
         content_associate_alt = .$`Which of the following content do you associate with the FT? (Select any that apply) - Other (please specify) - Text`,
         content_interested = .$`Which of the following content are you most interested in personally? - Selected Choice`,
         content_interested_alt = .$`Which of the following content are you most interested in personally? - Other (please specify) - Text`,
         three_words = .$`How would you describe the FT in three words?`,
         hold_sub = .$`Have you ever held an FT subscription?`,
         further_research = .$`We would like to invite you to take part in further research with the FT. If you would be interested in participating please indicate below.`,
         country = country) %>% 
  select(date, social_from, social_follow, follow_reason, follow_reason_alt, content_associate,
         content_associate_alt, content_interested, content_interested_alt, three_words,
         hold_sub, country) %>% 
  mutate(follow_reason = recode(follow_reason, 
                                "To keep up with the latest headlines" = "Latest headlines",
                                "To read the FT's take on the news" = "FT's take",
                                "To connect or converse with the FT community" = "FT community",
                                "To find stories on a specific topic the FT covers" = "Specific topics",
                                "To find stories relevant to my work / professional development" = "Professional development",
                                "To find material I might be inspired to read" = "Inspiring material",
                                "Other (please specify)" = "Other"),
         hold_sub = recode(hold_sub,
                           "I signed up for a trial offer in the past, but did not continue" = "Lapsed trialist",
                           "I used to have an FT subscription, but have since cancelled" = "Former subscriber",
                           "I'm currently an FT subscriber" = "Current subscriber",
                           "No" = "Never subscribed")) 
```


#Which social media source do we have the most responses from?

```{r}
ds %>% 
  count(social_from, sort = T) %>% 
  mutate(prop = n / sum(n)) %>% 
  ggplot(aes(ymax=cumsum(prop), ymin= c(0, head(cumsum(prop), n = -1)), xmax=4, xmin=3, fill = social_from, - prop)) +
  geom_rect(col = "black") +
  scale_fill_manual(values = cbPalette[2:5]) +
  coord_polar(theta="y", start = 0) +
  xlim(c(2, 4)) +
  geom_text(x = 2.7, aes(y=cumsum(prop) - 0.5 * prop, label = percent(prop,1), size = 4)) +
  theme_void() +
  theme(legend.position = "none")
```

# Have you ever held an FT subscription?

```{r}
ds %>% 
  select(hold_sub) %>% 
  count(hold_sub) %>% 
  drop_na() %>% 
  mutate(prop = n / sum(n)) %>% 
  ggplot(aes(reorder(hold_sub, + prop), prop, fill = hold_sub, label = percent(prop, 1))) +
  geom_col(show.legend = F) +
  geom_text(hjust = 1) +
  scale_y_continuous(labels = percent_format(1)) +
  coord_flip() +  
  scale_fill_manual(values = cbPalette[2:5],
                    breaks = c("Former subscriber", "Lapsed trialist", "Current subscriber",
                                  "Non-subscriber")) +
  labs(x = "Subscription type",
       y = "Percentage of Respondents",
       subtitle = "Have you ever held an FT subscription?",
       title = "Non-subscribers made up only 43% of social media followers\nwho engaged with this survey") +
  theme_minimal()
```

# Do different platforms have differing proportions of subs - non subs?

```{r, fig.width=10}
ds %>% 
  select(hold_sub, social_follow) %>% 
  mutate(person = row_number(),
         social_follow = str_split(social_follow, ",")) %>% 
  unnest(cols = c(social_follow)) %>% 
  group_by(person) %>%
  pivot_wider(names_from = 2,
              values_from = 2) %>% 
  ungroup() %>% 
  mutate_at(3:9,
             ~if_else(is.na(.x), 0, 1)) %>% 
  select(1, 3:7) %>% 
  group_by(hold_sub) %>% 
  summarise_at(1:5,
               ~sum(.), na.rm = T) %>% 
  drop_na() %>% 
  pivot_longer(2:6) %>% 
  group_by(name) %>% 
  mutate(prop = value / sum(value),
         alpha = if_else(hold_sub == "Never subscribed", 1, 0)) %>% 
{  ggplot(., aes(factor(name, levels = rev(c("Instagram", "Facebook", "YouTube",
                                             "Twitter", "LinkedIn"))), prop, 
                 fill = factor(hold_sub, levels = c("Lapsed trialist",
                                                    "Former subscriber",
                                                    "Current subscriber",
                                                    "Never subscribed")),
                 alpha = alpha, label = percent(prop, 1))) +
    geom_col() +
    geom_text(data = subset(., alpha == 1), position = position_stack(), hjust = 1,
              aes(y = .2)) +
    scale_fill_manual(values = cbPalette[2:5],
                      breaks = c("Lapsed trialist", "Former subscriber", "Current subscriber",
                                  "Never subscribed"),
                      labels = c("Lapsed trialist", "Former subscriber", "Current subscriber",
                                  "Never subscribed"))  +
    scale_alpha(range = c(.4,1)) +
    scale_y_continuous(labels = percent_format(1)) +
    coord_flip() +
    guides(alpha = F,
           fill = guide_legend(reverse = T, label.position = "bottom")) +
    labs(fill = "Subscriber type",
         y = "Percentage of Respondents", 
         x = "Social media followers",
         subtitle = "Susbcriber types of our followers from different social media platforms",
         title = "Non-subscribers are more likely to follow us on Instagram & Facebook") +
    theme_minimal() +
    theme(legend.position = "bottom")
}

ds %>% 
  select(hold_sub, social_follow) %>% 
  mutate(person = row_number(),
         social_follow = str_split(social_follow, ",")) %>% 
  unnest(cols = c(social_follow)) %>% 
  group_by(person) %>%
  pivot_wider(names_from = 2,
              values_from = 2) %>% 
  ungroup() %>% 
  mutate_at(3:9,
             ~if_else(is.na(.x), 0, 1)) %>% 
  select(1, 3:7) %>% 
  group_by(hold_sub) %>% 
  summarise_at(1:5,
               ~sum(.), na.rm = T) %>% 
  drop_na() %>% 
  pivot_longer(2:6) %>% 
  group_by(name) %>% 
  mutate(prop = value / sum(value),
         alpha = if_else(hold_sub == "Current subscriber", 1, 0)) %>% 
{  ggplot(., aes(factor(name, levels = rev(c("Instagram", "Facebook", "YouTube",
                                             "Twitter", "LinkedIn"))), prop, 
                 fill = factor(hold_sub, levels = c("Lapsed trialist",
                                                    "Former subscriber",
                                                    "Current subscriber",
                                                    "Never subscribed")),
                 alpha = alpha, label = percent(prop, 1))) +
    geom_col() +
    geom_text(data = subset(., alpha == 1), position = position_stack(), hjust = 1,
              aes(y = .6)) +
    scale_fill_manual(values = cbPalette[2:5],
                      breaks = c("Lapsed trialist", "Former subscriber", "Current subscriber",
                                  "Never subscribed"),
                      labels = c("Lapsed trialist", "Former subscriber", "Current subscriber",
                                  "Never subscribed")) +
    scale_alpha(range = c(.4,1)) +
    scale_y_continuous(labels = percent_format(1)) +
    coord_flip() +
    guides(alpha = F,
           fill = guide_legend(reverse = T, label.position = "bottom")) +
    labs(fill = "Subscriber type",
         y = "Percentage of Respondents", 
         x = "Social media followers",
         subtitle = "Susbcriber types of our followers from different social media platforms",
         title = "Current subscribers are more likely to follow us on Twitter, YouTube, & LinkedIn") +
    theme_minimal() +
    theme(legend.position = "bottom")
  }


```

# Which social media channels do users follow us on?

```{r}
social_media_follows <- ds %>% 
  select(social_follow) %>% 
  mutate(person = row_number(),
    social_follow = str_split(social_follow, ",")) %>% 
  unnest(cols = c(social_follow)) %>% 
  count(social_follow) %>% 
  drop_na()#%>% 
  #filter(social_follow %in% c("Facebook", "Instagram", "LinkedIn", "YouTube"))

```







# Do people follow on one or multiple channels?

```{r}

ds %>% 
  select(social_follow) %>% 
  mutate(person = row_number(),
    social_follow = str_split(social_follow, ",")) %>% 
  unnest(cols = c(social_follow)) %>% 
  group_by(person) %>%
  pivot_wider(names_from = 1,
              values_from = 1) %>% 
  ungroup() %>% 
  mutate_if(~!is.integer(.x),
             ~if_else(is.na(.x), 0, 1)) %>% 
  select(1:6, 8) %>% 
  group_by(person) %>% 
  mutate(total_socials = sum(Facebook, LinkedIn, Instagram, Twitter, YouTube, Telegram)) %>% 
  ungroup() %>% 
  summarise(mean(total_socials),
            median(total_socials))
  
```






# Overlap of Audiences

```{r}
library(reshape2)

exclusive_follows <- ds %>% 
  select(social_follow) %>% 
  mutate(person = row_number(),
    social_follow = str_split(social_follow, ",")) %>% 
  unnest(cols = c(social_follow)) %>% 
  group_by(person) %>%
  pivot_wider(names_from = 1,
              values_from = 1) %>% 
  ungroup() %>% 
  mutate_if(~!is.integer(.x),
             ~if_else(is.na(.x), 0, 1)) %>% 
  select(1:6) %>%
  ungroup() %>% 
  group_by(person) %>% 
  mutate(total_socials = sum(Facebook, LinkedIn, Instagram, Twitter, YouTube)) %>% 
  filter(total_socials ==1) %>% 
  pivot_longer(2:6) %>% 
  filter(value == 1) %>% 
  group_by(name) %>% 
  summarise(value = sum(value)) %>% 
  mutate(total_value = c(158, 370, 153, 283, 53)) %>% 
  mutate(prop = value / total_value) %>% 
  mutate(Var1 = name,
         Var2 = "Exclusively to one\n platform", 
         value = round(prop, 2) * 100) %>% 
  select(Var1, Var2, value)

social_array <- ds %>% 
  select(social_follow) %>% 
  mutate(person = row_number(),
    social_follow = str_split(social_follow, ",")) %>% 
  unnest(cols = c(social_follow)) %>% 
  group_by(person) %>%
  pivot_wider(names_from = 1,
              values_from = 1) %>% 
  ungroup() %>% 
  mutate_if(~!is.integer(.x),
             ~if_else(is.na(.x), 0, 1)) %>% 
  select(2:6) %>% 
  as.matrix() %>% 
  crossprod() 

floor(social_array * 100 / diag(social_array)) 

floor(social_array * 100 / diag(social_array)) %>% 
  melt() %>% 
  mutate(Var1 = factor(Var1, levels = c("YouTube", "LinkedIn", "Facebook",
                                        "Instagram", "Twitter")),
         Var2 = factor(Var2, levels = c("YouTube", "LinkedIn", "Facebook",
                                        "Instagram", "Twitter"))) %>% 
  mutate(Var2 = paste0("Also follow us on\n", Var2)) %>% 
  full_join(exclusive_follows) %>% 
{  ggplot(., aes(Var2, Var1, fill = Var1, label = paste0(value, "%"))) +
    geom_tile(show.legend = F) +
    geom_text(data = subset(., value !=100), col = "white",
              aes(size = value),
              show.legend = F) +
    scale_size_continuous(range = c(3,6)) +
    scale_y_discrete(limits = c("YouTube", "LinkedIn", "Facebook", "Instagram",
                                "Twitter")) +
    scale_x_discrete(position = "top", limits = c("Exclusively to one\n platform",
                                                  "Also follow us on\nTwitter",
                                                  "Also follow us on\nInstagram", 
                                                  "Also follow us on\nFacebook", 
                                                  "Also follow us on\nLinkedIn",
                                                  "Also follow us on\nYouTube" )) +
    scale_fill_manual(breaks = c("YouTube", "Twitter", "LinkedIn",
                                 "Instagram", "Facebook"),
                      values = c("#D55E00", "#56B4E9", "#009E73",
                                 "#CC79A7", "#0072B2")) +
    labs(x = "",
         y = "Social Media Platform",
         subtitle = "Examining the platform crossover from our social media following",
         title = "Followers on Twitter & Instagram tend to stick to one platform") +
    theme_minimal()
}


```

# What is your main reason for following the FT on social media?

```{r, fig.width=10}
ds %>% 
  select(social_follow, follow_reason) %>% 
  mutate(social_follow = str_split(social_follow, ",")) %>% 
  unnest(cols = c(social_follow)) %>% 
  filter(!social_follow %in% c("I don't follow the FT on any social channels", "Telegram")) %>% 
  group_by(social_follow, follow_reason) %>% 
  summarise(n = n()) %>% 
  drop_na() %>% 
  mutate(prop = n / sum(n),
         alpha = if_else(follow_reason == "Latest headlines", 1, 0)) %>% 
{  ggplot(., aes(social_follow, prop, fill = reorder(follow_reason, - prop),
                 label = percent(prop,1 ),
                 alpha  = alpha)) +
    geom_col(show.legend = T) +
    scale_fill_manual(values = cbPalette[2:8]) +
    scale_alpha(range = c(.4,1)) +
    geom_text(data = subset(., alpha == 1),
              vjust = 1, aes(y = .8)) +
    scale_y_continuous(labels = percent_format()) +
    guides(alpha = F) +
    labs(fill = "Primary follow reason",
         x = "Social Media",
         y = "Percentage of followers",
         title = "Keeping up with the latest headlines is the most stated reason for following",
         subtitle = "What is your main reason for following the FT on social media?") +
    theme_minimal()
}



ds %>% 
  select(social_follow, follow_reason) %>% 
  mutate(social_follow = str_split(social_follow, ",")) %>% 
  unnest(cols = c(social_follow)) %>% 
  filter(!social_follow %in% c("I don't follow the FT on any social channels", "Telegram")) %>% 
  group_by(social_follow, follow_reason) %>% 
  summarise(n = n()) %>% 
  drop_na() %>% 
  mutate(prop = n / sum(n),
         alpha = if_else(follow_reason == "FT's take", 1, 0)) %>% 
{  ggplot(., aes(social_follow, prop, fill = reorder(follow_reason, - prop),
                 label = percent(prop,1 ),
                 alpha  = alpha)) +
    geom_col(show.legend = T) +
    scale_fill_manual(values = cbPalette[2:8]) +
    scale_alpha(range = c(.4,1)) +
    geom_text(data = subset(., alpha == 1),
              vjust = 1, aes(y = .58)) +
    scale_y_continuous(labels = percent_format()) +
    guides(alpha = F) +
    labs(fill = "Primary follow reason",
         x = "Social Media",
         y = "Percentage of followers",
         title = "Facebook users are comparatively more interested in the FT's take",
         subtitle = "What is your main reason for following the FT on social media?") +
    theme_minimal()
}



ds %>% 
  select(social_follow, follow_reason) %>% 
  mutate(social_follow = str_split(social_follow, ",")) %>% 
  unnest(cols = c(social_follow)) %>% 
  filter(!social_follow %in% c("I don't follow the FT on any social channels", "Telegram")) %>% 
  group_by(social_follow, follow_reason) %>% 
  summarise(n = n()) %>% 
  drop_na() %>% 
  mutate(prop = n / sum(n),
         alpha = if_else(follow_reason == "Inspiring material", 1, 0)) %>% 
{  ggplot(., aes(social_follow, prop, fill = reorder(follow_reason, - prop),
                 label = percent(prop,1 ),
                 alpha  = alpha)) +
    geom_col(show.legend = T) +
    scale_fill_manual(values = cbPalette[2:8]) +
    scale_alpha(range = c(.4,1)) +
    geom_text(data = subset(., alpha == 1),
              vjust = 1, aes(y = .36)) +
    scale_y_continuous(labels = percent_format()) +
    guides(alpha = F) +
    labs(fill = "Primary follow reason",
         x = "Social Media",
         y = "Percentage of followers",
         title = "YouTube users are more interested in finding inspiring material",
         subtitle = "What is your main reason for following the FT on social media?") +
    theme_minimal()
}

ds %>% 
  select(social_follow, follow_reason) %>% 
  mutate(social_follow = str_split(social_follow, ",")) %>% 
  unnest(cols = c(social_follow)) %>% 
  filter(!social_follow %in% c("I don't follow the FT on any social channels", "Telegram")) %>% 
  group_by(social_follow, follow_reason) %>% 
  summarise(n = n()) %>% 
  drop_na() %>% 
  mutate(prop = n / sum(n),
         alpha = if_else(follow_reason == "Professional development", 1, 0)) %>% 
{  ggplot(., aes(social_follow, prop, fill = reorder(follow_reason, - prop),
                 label = percent(prop,1 ),
                 alpha  = alpha)) +
    geom_col(show.legend = T) +
    scale_fill_manual(values = cbPalette[2:8]) +
    scale_alpha(range = c(.4,1)) +
    geom_text(data = subset(., alpha == 1),
              vjust = 1, aes(y = .18)) +
    scale_y_continuous(labels = percent_format()) +
    guides(alpha = F) +
    labs(fill = "Primary follow reason",
         x = "Social Media",
         y = "Percentage of followers",
         title = "LinkedIn users are more likely to follow us to aid in their work & professional development",
         subtitle = "What is your main reason for following the FT on social media?") +
    theme_minimal()
}
```


```{r}

ds %>% 
  select(social_follow, follow_reason) %>% 
  mutate(social_follow = str_split(social_follow, ",")) %>% 
  unnest(cols = c(social_follow)) %>% 
  group_by(social_follow, follow_reason) %>% 
  summarise(n = n()) %>% 
  drop_na() %>% 
  mutate(prop = n / sum(n)) %>% 
  select(1,2,4) %>% 
  pivot_wider(names_from = follow_reason,
              values_from = prop) %>% 
  drop_na() %>% 
  ungroup() %>% 
  select(2:8) %>% 
  cor() %>% 
  dist() %>% 
  hclust() %>% 
  plot()

```

# What content is associated with the FT?

```{r}
ds %>% 
  select(content_associate) %>% 
  drop_na() %>% 
  mutate(person = row_number(),
         content_associate = str_split(content_associate, ",")) %>% 
  unnest(cols = c(content_associate)) %>% 
  group_by(content_associate) %>% 
  summarise(n = n()) %>%
  arrange(-n) %>% 
  mutate(prop = n / 654)

```


# Do followers from different social platforms associate the FT with different content? 

```{r,fig.width=10}
ds %>% 
  select(social_follow, content_associate) %>% 
    mutate(person = row_number(),
      social_follow = str_split(social_follow, ","),
      content_associate = str_split(content_associate, ",")) %>% 
  unnest(cols = social_follow) %>% 
  unnest(cols = content_associate) %>% 
  group_by(content_associate, social_follow) %>% 
  summarise(n = n()) %>% 
  drop_na() %>% 
  ungroup() %>% 
  left_join(social_media_follows, by = c("social_follow")) %>% 
  mutate(prop = n.x / n.y,
         alpha = if_else(content_associate %in% c("Finance & Markets",
                                                         "Companies",
                                                         "World news",
                                                         "Politics"), 1, 0),
         label = if_else(social_follow == "YouTube", 
                         paste0(content_associate, '\n', percent(prop, 1)),
                         percent(prop, 1))) %>% 
  filter(social_follow %in% c("Facebook", "Instagram", "LinkedIn", "YouTube")) %>% 
{  ggplot(., aes(social_follow, prop, col = reorder(content_associate, + prop),
              alpha = alpha)) +
      geom_text_repel(data = subset(., alpha ==1), aes(label = label, col = content_associate),
                      show.legend = F) +
    coord_flip() +
    geom_point(show.legend = F) +
    guides(alpha = F) 
  }
  


```



